---
title: "Spotify R"
author: "Austin Spivey"
date: "2/8/2019"
output: html_document
---

Set up.

```{r}
#install.packages("httr")

library(httr)
```


Grab my playlists in order to identify the Playlist IDs of the two 'The Daily' playlists.

First, grabbing raw data from the Spotify API:

```{r}
auth = "BQAxZBPvS0UoQ2URIbbC-6w9iNu2Qt2j2k0TIfPlce_PQAK3r4B6DEQlgwuRzCigy93S-DQrbbO7T2s5jJNnhDO1o8Ut0wf72GWp1H3WoX9ValayBVioinpXdo2Rumq3HYqkcDtaMPSMkp2CfzcZ2UlLRCx7RA"
url = "https://api.spotify.com/v1/users/aspives/playlists"
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
```


Get Playlist IDs:

```{r}
PL_df = data.frame("ID" = character(), "Name" = character(), stringsAsFactors = FALSE)

for ( x in 1:length(body[["items"]]) ) {
  if(length(grep("(daily)", body[["items"]][[x]][["name"]], ignore.case = TRUE)) > 0) {
    PL_df[x,] = c(body[["items"]][[x]][["name"]], body[["items"]][[x]][["id"]])
  }
}

PL_df = na.omit(PL_df)
```


Now we can use the IDs in another Spotify API call to grab the track, artist, metadata, and other information in each one.

Get track info:

```{r}
auth = "BQAxZBPvS0UoQ2URIbbC-6w9iNu2Qt2j2k0TIfPlce_PQAK3r4B6DEQlgwuRzCigy93S-DQrbbO7T2s5jJNnhDO1o8Ut0wf72GWp1H3WoX9ValayBVioinpXdo2Rumq3HYqkcDtaMPSMkp2CfzcZ2UlLRCx7RA"



track_df = data.frame("MasterRow" = integer(), "Playlist ID" = character(), "Playlist Name" = character(), "Added At" = character(), "Added By" = character(), "Album" = character(), "Album ID" = character(), "Album Type" = character(), "Album Release Date" = character(), "Artist" = character(), "Artist ID" = character(), "Explicit" = character(), "ISRC" = character(), "Song ID" = character(), "Song Title" = character(), "Song Popularity" = character(), "Duration (ms)" = character(), "Is Playable" = character(), stringsAsFactors = FALSE)


for ( y in 1:nrow(PL_df)){

offset = 0
stop = 0

while (stop == 0) {

url = paste0("https://api.spotify.com/v1/playlists/", PL_df[y,2], "/tracks?market=US&limit=100&offset=", offset)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")




  for ( x in 1:length(body[["items"]]) ) {
    for (a in 1:length(body[["items"]][[x]][["track"]][["artists"]])) {
    track_df[nrow(track_df)+1,] = c(
                          # MasterRow
                          nrow(track_df)+1,
                          # Playlist ID
                          PL_df[y,2],
                          # Playlist Name
                          PL_df[y,1],
                          # Added At
                          body[["items"]][[x]][["added_at"]],
                          # Added By
                          body[["items"]][[x]][["added_by"]][["id"]],
                          # Album
                          body[["items"]][[x]][["track"]][["album"]][["name"]],
                          # Album ID
                          body[["items"]][[x]][["track"]][["album"]][["id"]],
                          # Album Type
                          body[["items"]][[x]][["track"]][["album"]][["album_type"]],
                          # Album Release Date
                          body[["items"]][[x]][["track"]][["album"]][["release_date"]],
                          # Artist
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["name"]],
                          # Artist ID
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["id"]],
                          # Explicit
                          body[["items"]][[x]][["track"]][["explicit"]],
                          # ISRC
                          body[["items"]][[x]][["track"]][["external_ids"]][["isrc"]],
                          # Song ID
                          body[["items"]][[x]][["track"]][["id"]],
                          # Song Title
                          body[["items"]][[x]][["track"]][["name"]],
                          # Song Popularity
                          body[["items"]][[x]][["track"]][["popularity"]],
                          # Duration (ms)
                          body[["items"]][[x]][["track"]][["duration_ms"]],
                          # Is Playable
                          body[["items"]][[x]][["track"]][["is_playable"]]
                          )
    }
  }


if (  !is.null(body[["next"]])){ 
  offset = offset + 100
} else {
    stop = 1
  }

}

}
```


Cross check numbers:

```{r}
length(unique(track_df[,4]))
```


The total song count between the two playlists is super close to being correct, but it looks like 2 of the songs in the playlists are unplayable for some reason, so let's ditch those:
```{r}
track_df = track_df[track_df$Is.Playable == TRUE, ]
```


Bring in artist info:

```{r}
auth = "BQAxZBPvS0UoQ2URIbbC-6w9iNu2Qt2j2k0TIfPlce_PQAK3r4B6DEQlgwuRzCigy93S-DQrbbO7T2s5jJNnhDO1o8Ut0wf72GWp1H3WoX9ValayBVioinpXdo2Rumq3HYqkcDtaMPSMkp2CfzcZ2UlLRCx7RA"

df_artists = track_df$Artist.ID

artists = ""

lank = 50

inn = 1


track_artists = data.frame("MasterRow" = "", "Artist ID" = "", "Artist Name" = "", "Artist Genre" = "", "Artist Popularity" = "", "Artist Followers" = "", stringsAsFactors = FALSE)

#while ( !is.na(track_artists$Artist.ID)){
 while ( lank <= (nrow(track_df) + 50)){

  if ( lank > nrow(track_df) ) { 
        lank = nrow(track_df)
      }
   
artists = ""

for ( p in inn:lank) { artists = paste0(artists,"%2C",df_artists[p])}

artists = substr(artists, 4, nchar(artists) - 3)
  
url = paste0("https://api.spotify.com/v1/artists?ids=", artists)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
  


  for ( x in 1:50 ) {
    for (a in 1:length(body[["artists"]][[x]][["genres"]])) {
    track_artists[nrow(track_artists)+1,] = c(
                          # MasterRow
                          nrow(track_artists)+1,
                          # Artist ID
                          body[["artists"]][[x]][["id"]],
                          # Artist Name
                          body[["artists"]][[x]][["name"]],
                          # Artist Genre
                          if ( length(body[["artists"]][[x]][["genres"]]) == 0 ) {NA} else {
                          body[["artists"]][[x]][["genres"]][[a]] },
                          # Artist Popularity
                          body[["artists"]][[x]][["popularity"]],
                          # Artist Followers
                          body[["artists"]][[x]][["followers"]][["total"]]
                          )
    }
  }

lank = lank + 50
inn = inn + 50

}
```











Bring in song audio analysis data:

```{r}
auth = "BQAxZBPvS0UoQ2URIbbC-6w9iNu2Qt2j2k0TIfPlce_PQAK3r4B6DEQlgwuRzCigy93S-DQrbbO7T2s5jJNnhDO1o8Ut0wf72GWp1H3WoX9ValayBVioinpXdo2Rumq3HYqkcDtaMPSMkp2CfzcZ2UlLRCx7RA"

df_songs = track_df$Song.ID

songs = ""

lank = 50

inn = 1


track_songs = data.frame("MasterRow" = integer(), "Song ID" = character(), "Danceability" = character(), "Energy" = character(), "Key" = character(), "Loudness" = character(), "Mode" = character(), "Speechiness" = character(), "Acousticness" = character(), "Instrumentalness" = character(), "Liveness" = character(), "Valence" = character(), "Tempo" = character(), "Type" = character(), "Time Signature" = character(), stringsAsFactors = FALSE)

#while ( !is.na(track_songs$Song.ID)){
 while ( lank <= (nrow(track_df) + 50)){

  if ( lank > nrow(track_df) ) { 
        lank = nrow(track_df)
      }
   
songs = ""

for ( p in inn:lank) { songs = paste0(songs,"%2C",df_songs[p])}

songs = substr(songs, 4, nchar(songs) - 3)
  
url = paste0("https://api.spotify.com/v1/audio-features?ids=", songs)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
  


  for ( x in 1:50 ) {
    track_songs[nrow(track_songs)+1,] = c(
                          # MasterRow
                          nrow(track_songs)+1,
                          # Song ID
                          body[["audio_features"]][[x]][["id"]],
                          # Danceability
                          body[["audio_features"]][[x]][["danceability"]],
                          # Energy
                          body[["audio_features"]][[x]][["energy"]],
                          # Key
                          body[["audio_features"]][[x]][["key"]],
                          # Loudness
                          body[["audio_features"]][[x]][["loudness"]],
                          # Mode
                          body[["audio_features"]][[x]][["mode"]],
                          # Speechiness
                          body[["audio_features"]][[x]][["speechiness"]],
                          # Acousticness
                          body[["audio_features"]][[x]][["acousticness"]],
                          # Instrumentalness
                          body[["audio_features"]][[x]][["instrumentalness"]],
                          # Liveness
                          body[["audio_features"]][[x]][["liveness"]],
                          # Valence
                          body[["audio_features"]][[x]][["valence"]],
                          # Tempo
                          body[["audio_features"]][[x]][["tempo"]],
                          # Type
                          body[["audio_features"]][[x]][["type"]],
                          # Time Signature
                         body[["audio_features"]][[x]][["time_signature"]]
                          )
  }

lank = lank + 50
inn = inn + 50

}
```







Cleaning our data:

```{r}
# Ditch some erroneous values that were brought in
track_songs = track_songs[nchar(track_songs$Song.ID) > 10, ]
```


Fix usernames:

```{r}
track_df$Our.Names = ""

for (g in 1:nrow(track_df)){
  if ( track_df[g,"Added.By"] == "aspives") {track_df[g,"Our.Names"] = "Austin" }
  if ( track_df[g,"Added.By"] == "will100dankos") {track_df[g,"Our.Names"] = "Will" }
  if ( track_df[g,"Added.By"] == "vddiiymmzfi9hasnn9tct6au2") {track_df[g,"Our.Names"] = "Tyler" }
  if ( track_df[g,"Added.By"] == "1230145895") {track_df[g,"Our.Names"] = "Alec" }
  if ( track_df[g,"Added.By"] == "1296143342") {track_df[g,"Our.Names"] = "Arnav" }
  if ( track_df[g,"Added.By"] == "12168315368") {track_df[g,"Our.Names"] = "Max" }
  if ( track_df[g,"Added.By"] == "bradpehr") {track_df[g,"Our.Names"] = "Brad" }
  if ( track_df[g,"Added.By"] == "kirkkovach") {track_df[g,"Our.Names"] = "Kirk" }
  if ( track_df[g,"Added.By"] == "rahollraholl") {track_df[g,"Our.Names"] = "Stephen" }
}
```



Get data on personal library

```{r}
auth = "BQD2OaC3aBoRLFw9a66Kcbt36VBBfN7R-rESMaFhJdmjW4zncnPrOyYf884Km2zz4GDG4bEUsdfM_9n8tyGd27CxwtrWqnhfKdNoeLXdj53_dM_9c_vefttIQEg6PL4oVfbJRC-bQeMMJD_-JZTRcwDJazXIdrxT9GztpQ"

your_username = "aspives"


track_library = data.frame("MasterRow" = integer(), "user" = character(), "Added At" = character(), "Album" = character(), "Album ID" = character(), "Album Type" = character(), "Album Release Date" = character(), "Artist" = character(), "Artist ID" = character(), "Explicit" = character(), "ISRC" = character(), "Song ID" = character(), "Song Title" = character(), "Song Popularity" = character(), "Duration (ms)" = character(), "Is Playable" = character(), stringsAsFactors = FALSE)

offset = 0
stop = 0

while (stop == 0) {

url = paste0("https://api.spotify.com/v1/me/tracks?market=US&limit=50&offset=0", offset)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")

  for ( x in 1:length(body[["items"]]) ) {
    for (a in 1:length(body[["items"]][[x]][["track"]][["artists"]])) {
    track_library[nrow(track_library)+1,] = c(
                          # MasterRow
                          nrow(track_library)+1,
                          # user
                          your_username,
                          # Added At
                          body[["items"]][[x]][["added_at"]],
                          # Added By
                          body[["items"]][[x]][["added_by"]][["id"]],
                          # Album
                          body[["items"]][[x]][["track"]][["album"]][["name"]],
                          # Album ID
                          body[["items"]][[x]][["track"]][["album"]][["id"]],
                          # Album Type
                          body[["items"]][[x]][["track"]][["album"]][["album_type"]],
                          # Album Release Date
                          body[["items"]][[x]][["track"]][["album"]][["release_date"]],
                          # Artist
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["name"]],
                          # Artist ID
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["id"]],
                          # Explicit
                          body[["items"]][[x]][["track"]][["explicit"]],
                          # ISRC
                          body[["items"]][[x]][["track"]][["external_ids"]][["isrc"]],
                          # Song ID
                          body[["items"]][[x]][["track"]][["id"]],
                          # Song Title
                          body[["items"]][[x]][["track"]][["name"]],
                          # Song Popularity
                          body[["items"]][[x]][["track"]][["popularity"]],
                          # Duration (ms)
                          body[["items"]][[x]][["track"]][["duration_ms"]],
                          # Is Playable
                          body[["items"]][[x]][["track"]][["is_playable"]]
                          )
    }
  }


if (  !is.null(body[["next"]])){ 
  offset = offset + 50
} else {
    stop = 1
  }

}
```




Genius API calls!

```{r}
auth = "vPRU-vpdXiXrDBVZTC4uur4GTvOE9GhShXdjopz5FkhvglwAc5vKRRDcDvKZyEx2"


track_genius = data.frame("MasterRow" = integer(), "Song Title" = character(), "Song Title with Feat" = character(), "Genius ID" = character(), "Hot" = character(), "Page Views" = character(), stringsAsFactors = FALSE)

# q = "Mile High"
# q = URLencode(q)

for (q in 1:nrow(track_df)) { 

url = paste0("https://api.genius.com/search?q=", URLencode(track_df[q,15]))
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")

  for ( x in 1:length(body[["items"]]) ) {
    for (a in 1:length(body[["items"]][[x]][["track"]][["artists"]])) {
    track_genius[nrow(track_genius)+1,] = c(
                          # MasterRow
                          nrow(track_genius)+1,
                          # Song Title
                          body[["response"]][["hits"]][[1]][["result"]][["title"]],
                          # Song Title with Feat
                          body[["response"]][["hits"]][[1]][["result"]][["title_with_featured"]],
                          # Genius ID
                          body[["response"]][["hits"]][[1]][["result"]][["id"]],
                          # Hot
                          body[["response"]][["hits"]][[1]][["result"]][["stats"]][["hot"]],
                          # Page Views
                          body[["response"]][["hits"]][[1]][["result"]][["stats"]][["pageviews"]]
                          )
    }
  }


if (  !is.null(body[["next"]])){ 
  offset = offset + 50
} else {
    stop = 1
  }

}
```






Output data frames to CSV:

```{r}
write.csv2(track_df, "/Users/austin/Documents/Data Stuff/Spotify Data project/track_df.csv")

write.csv2(track_artists, "/Users/austin/Documents/Data Stuff/Spotify Data project/track_artists.csv")

write.csv2(track_songs, "/Users/austin/Documents/Data Stuff/Spotify Data project/track_songs.csv")

write.csv2(track_library, "/Users/austin/Documents/Data Stuff/Spotify Data project/track_library.csv")
```


```{r}
auth = "vPRU-vpdXiXrDBVZTC4uur4GTvOE9GhShXdjopz5FkhvglwAc5vKRRDcDvKZyEx2"

track_genius = data.frame("MasterRow" = integer(), "Song Title" = character(), "Song Title with Feat" = character(), "Artist" = character(), "Genius ID" = character(), "Searched Song" = character(), "Searched Song Spotify ID" = character(), "Hot" = character(), "Page Views" = character(), stringsAsFactors = FALSE)

all_artists = c()


for (q in 1:nrow(track_df)) {
# for (q in 1:7) {
    
if ( track_df[q, 14] == if( is.na(track_df[q+1, 14]) ){
  "@~darth@@"
  
  } else {track_df[q+1, 14]} ) {
  all_artists[length(all_artists)+1] = track_df[q, 10]
  next} else {
    all_artists[length(all_artists)+1] = track_df[q, 10]
    query = paste0(track_df[q,15], " ", paste(all_artists, collapse = ' '))
    query_url = URLencode(query)
    
    url = paste0("https://api.genius.com/search?q=", query_url)
    r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
    body = content(r, as = "parsed")
    
    if ( length(body[["response"]][["hits"]]) == 0) {
      track_genius[nrow(track_genius)+1,] = c(nrow(track_genius)+1,all_artists,NA,NA,NA,NA,NA,NA,NA)
      next
    }


    track_genius[nrow(track_genius)+1,] = c(
                          # MasterRow
                          nrow(track_genius)+1,
                          # Song Title
                          body[["response"]][["hits"]][[1]][["result"]][["title"]],
                          # Song Title with Feat
                          body[["response"]][["hits"]][[1]][["result"]][["title_with_featured"]],
                          # Artist
                          body[["response"]][["hits"]][[1]][["result"]][["primary_artist"]][["name"]],
                          # Genius ID
                          body[["response"]][["hits"]][[1]][["result"]][["id"]],
                          # Searched Song
                          query,
                          # Searched Song Spotify ID
                          track_df[q, 14],
                          # Hot
                          body[["response"]][["hits"]][[1]][["result"]][["stats"]][["hot"]],
                          # Page Views
                          if(is.null(body[["response"]][["hits"]][[1]][["result"]][["stats"]][["pageviews"]])) {
                            NA
                          } else{
                          body[["response"]][["hits"]][[1]][["result"]][["stats"]][["pageviews"]]
                          }
                          )
    
    all_artists = c()

    
    
    
    }
}


```




```{r}



```

