---
title: "Spotify R"
author: "Austin Spivey"
date: "2/8/2019"
output: html_document
---

Set up.

```{r}
#install.packages("httr")

library(httr)
```


Grab my playlists in order to identify the Playlist IDs of the two 'The Daily' playlists.

First, grabbing raw data from the Spotify API:

```{r}
auth = "BQBDe1-bio2xKiua7_ZfRFcgRP7iKLxI--QQWcrg4eFsiAmwJpoT9MV4J9dCouSU1i-0Qe3nMwRDUYeP4-i2-FVKGPn0eNQOt21hDNndPtx4BvM1DitY0yQI1fQiPgyfnwfS9D5diup3x6OcJnLq1tlAiQS69Q"
url = "https://api.spotify.com/v1/users/aspives/playlists"
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
```


Get Playlist IDs:

```{r}
PL_df = data.frame("ID" = character(), "Name" = character(), stringsAsFactors = FALSE)

for ( x in 1:length(body[["items"]]) ) {
  if(length(grep("(daily)", body[["items"]][[x]][["name"]], ignore.case = TRUE)) > 0) {
    PL_df[x,] = c(body[["items"]][[x]][["name"]], body[["items"]][[x]][["id"]])
  }
}

PL_df = na.omit(PL_df)
```


Now we can use the IDs in another Spotify API call to grab the track, artist, metadata, and other information in each one.

Get track info:

```{r}
auth = "BQAdaBHOtuIkUaTiRU6IiulvwIbBeDuyZ-F-52EzJSLfBVTCVZb7PRt_nmzq6mgLprLuYAagv_BJoOueGC-w0mqfX_j6d2EAXvcrCP5gpVHLS3-UsT_MinOZOG9J6rWI6GOi_ffP4baXkqsge6RsByTDZNK_7Q"



track_df = data.frame("MasterRow" = integer(), "Playlist ID" = character(), "Playlist Name" = character(), "Added At" = character(), "Added By" = character(), "Album" = character(), "Album ID" = character(), "Album Type" = character(), "Album Release Date" = character(), "Artist" = character(), "Artist ID" = character(), "Explicit" = character(), "ISRC" = character(), "Song ID" = character(), "Song Title" = character(), "Song Popularity" = character(), "Duration (ms)" = character(), "Is Playable" = character(), stringsAsFactors = FALSE)


for ( y in 1:nrow(PL_df)){

offset = 0
stop = 0

while (stop == 0) {

url = paste0("https://api.spotify.com/v1/playlists/", PL_df[y,2], "/tracks?market=US&limit=100&offset=", offset)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")




  for ( x in 1:length(body[["items"]]) ) {
    for (a in 1:length(body[["items"]][[x]][["track"]][["artists"]])) {
    track_df[nrow(track_df)+1,] = c(
                          # MasterRow
                          nrow(track_df)+1,
                          # Playlist ID
                          PL_df[y,2],
                          # Playlist Name
                          PL_df[y,1],
                          # Added At
                          body[["items"]][[x]][["added_at"]],
                          # Added By
                          body[["items"]][[x]][["added_by"]][["id"]],
                          # Album
                          body[["items"]][[x]][["track"]][["album"]][["name"]],
                          # Album ID
                          body[["items"]][[x]][["track"]][["album"]][["id"]],
                          # Album Type
                          body[["items"]][[x]][["track"]][["album"]][["album_type"]],
                          # Album Release Date
                          body[["items"]][[x]][["track"]][["album"]][["release_date"]],
                          # Artist
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["name"]],
                          # Artist ID
                          body[["items"]][[x]][["track"]][["artists"]][[a]][["id"]],
                          # Explicit
                          body[["items"]][[x]][["track"]][["explicit"]],
                          # ISRC
                          body[["items"]][[x]][["track"]][["external_ids"]][["isrc"]],
                          # Song ID
                          body[["items"]][[x]][["track"]][["id"]],
                          # Song Title
                          body[["items"]][[x]][["track"]][["name"]],
                          # Song Popularity
                          body[["items"]][[x]][["track"]][["popularity"]],
                          # Duration (ms)
                          body[["items"]][[x]][["track"]][["duration_ms"]],
                          # Is Playable
                          body[["items"]][[x]][["track"]][["is_playable"]]
                          )
    }
  }


if (  !is.null(body[["next"]])){ 
  offset = offset + 100
} else {
    stop = 1
  }

}

}
```


Cross check numbers:

```{r}
length(unique(track_df[,4]))
```


The total song count between the two playlists is super close to being correct, but it looks like 2 of the songs in the playlists are unplayable for some reason, so let's ditch those:
```{r}
track_df = track_df[track_df$Is.Playable == TRUE, ]
```


Bring in artist info:

```{r}
auth = "BQAdaBHOtuIkUaTiRU6IiulvwIbBeDuyZ-F-52EzJSLfBVTCVZb7PRt_nmzq6mgLprLuYAagv_BJoOueGC-w0mqfX_j6d2EAXvcrCP5gpVHLS3-UsT_MinOZOG9J6rWI6GOi_ffP4baXkqsge6RsByTDZNK_7Q"

df_artists = track_df$Artist.ID

artists = ""

lank = 50

inn = 1


track_artists = data.frame("MasterRow" = "", "Artist ID" = "", "Artist Name" = "", "Artist Genre" = "", "Artist Popularity" = "", "Artist Followers" = "", stringsAsFactors = FALSE)

#while ( !is.na(track_artists$Artist.ID)){
 while ( lank <= (nrow(track_df) + 50)){

  if ( lank > nrow(track_df) ) { 
        lank = nrow(track_df)
      }
   
artists = ""

for ( p in inn:lank) { artists = paste0(artists,"%2C",df_artists[p])}

artists = substr(artists, 4, nchar(artists) - 3)
  
url = paste0("https://api.spotify.com/v1/artists?ids=", artists)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
  


  for ( x in 1:50 ) {
    for (a in 1:length(body[["artists"]][[x]][["genres"]])) {
    track_artists[nrow(track_artists)+1,] = c(
                          # MasterRow
                          nrow(track_artists)+1,
                          # Artist ID
                          body[["artists"]][[x]][["id"]],
                          # Artist Name
                          body[["artists"]][[x]][["name"]],
                          # Artist Genre
                          if ( length(body[["artists"]][[x]][["genres"]]) == 0 ) {NA} else {
                          body[["artists"]][[x]][["genres"]][[a]] },
                          # Artist Popularity
                          body[["artists"]][[x]][["popularity"]],
                          # Artist Followers
                          body[["artists"]][[x]][["followers"]][["total"]]
                          )
    }
  }

lank = lank + 50
inn = inn + 50

}
```











Bring in song audio analysis data:

```{r}
auth = "BQCj797c9viisZ1_cmbqfnf_MGZLnQxxK4eavtPoJ13xrbN-EUoinSdKRAMTLEdGu-hBZPYZnrRmp__yHv1YKbKNcY1Y8XYDTOXTX3pCZY9Cpu0X36FN678-tmV2veQQnXUNRxa3e6VJp77aPinOJBs8yEb_gA"

df_songs = track_df$Song.ID

songs = ""

lank = 50

inn = 1


track_songs = data.frame("MasterRow" = integer(), "Song ID" = character(), "Danceability" = character(), "Energy" = character(), "Key" = character(), "Loudness" = character(), "Mode" = character(), "Speechiness" = character(), "Acousticness" = character(), "Instrumentalness" = character(), "Liveness" = character(), "Valence" = character(), "Tempo" = character(), "Type" = character(), "Time Signature" = character(), stringsAsFactors = FALSE)

#while ( !is.na(track_songs$Song.ID)){
 while ( lank <= (nrow(track_df) + 50)){

  if ( lank > nrow(track_df) ) { 
        lank = nrow(track_df)
      }
   
songs = ""

for ( p in inn:lank) { songs = paste0(songs,"%2C",df_songs[p])}

songs = substr(songs, 4, nchar(songs) - 3)
  
url = paste0("https://api.spotify.com/v1/audio-features?ids=", songs)
r = GET(url, add_headers("Authorization" = paste0("Bearer ", auth)))
body = content(r, as = "parsed")
  


  for ( x in 1:50 ) {
    track_songs[nrow(track_songs)+1,] = c(
                          # MasterRow
                          nrow(track_songs)+1,
                          # Song ID
                          body[["audio_features"]][[x]][["id"]],
                          # Danceability
                          body[["audio_features"]][[x]][["danceability"]],
                          # Energy
                          body[["audio_features"]][[x]][["energy"]],
                          # Key
                          body[["audio_features"]][[x]][["key"]],
                          # Loudness
                          body[["audio_features"]][[x]][["loudness"]],
                          # Mode
                          body[["audio_features"]][[x]][["mode"]],
                          # Speechiness
                          body[["audio_features"]][[x]][["speechiness"]],
                          # Acousticness
                          body[["audio_features"]][[x]][["acousticness"]],
                          # Instrumentalness
                          body[["audio_features"]][[x]][["instrumentalness"]],
                          # Liveness
                          body[["audio_features"]][[x]][["liveness"]],
                          # Valence
                          body[["audio_features"]][[x]][["valence"]],
                          # Tempo
                          body[["audio_features"]][[x]][["tempo"]],
                          # Type
                          body[["audio_features"]][[x]][["type"]],
                          # Time Signature
                         body[["audio_features"]][[x]][["time_signature"]]
                          )
  }

lank = lank + 50
inn = inn + 50

}
```







Cleaning our data:

```{r}
# Ditch some erroneous values that were brought in
track_df = track_songs[nchar(track_songs$Song.ID) > 10, ]
```



Output data frames to CSV:

```{r}
write.csv2(track_df, "/Users/austin/Documents/Data Stuff/Spotify R project/track_df.csv")

write.csv2(track_artists, "/Users/austin/Documents/Data Stuff/Spotify R project/track_artists.csv")

write.csv2(track_songs, "/Users/austin/Documents/Data Stuff/Spotify R project/track_songs.csv")
```

